### 2013-06-04 poster/poster.tex
wrong font
final model feature count
brown only

\begin{description}
\item [Part-of-speech (POS) $n$-grams] Counts of every POS 1-, 2-, and 3-gram in each document. %53.92\% 
\item [FreqChar] Counts of character 1--4-grams that are observed more than 5 times in the training corpus.
\item [CharPrompt] Conjunction of the FreqChar features with the prompt ID %65.09
\item [Brown clusters] We clustered 8~billion words of English into 600~clusters and used 1--4-grams.
\item[PsvRatio] The proportion of passive verbs out of all verbs.
\item[DocLen] Document length in tokens.
\item[Punct] Counts of each punctuation mark. 
\item[Misspell] Spelling correction edits. Features included substitutions, deletions, insertions and joinings.% as well as the word position where the error occurred.
\item[\feat{Restore}] Substitutions, deletions and
  insertions of common words that were restored with an $n$-gram LM.
\item[CxtFxn] Contextual function words. Counts of $n$-grams consisting of one or two function words and the POS tag of the adjacent words: {\tt CHI:<some JJ>}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Results%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Results}{name=results,column=1.15,span=1.85,below=example}{
\begin{center}
\small
\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r||c|c|}
      %\hline
 \multicolumn{1}{c}{} & \multicolumn{1}{c}{ARA} & \multicolumn{1}{c}{CHI} & \multicolumn{1}{c}{FRE} & \multicolumn{1}{c}{GER} 
 & \multicolumn{1}{c}{HIN} & \multicolumn{1}{c}{ITA} & \multicolumn{1}{c}{JPN} &  \multicolumn{1}{c}{KOR} & \multicolumn{1}{c}{SPA} 
 &  \multicolumn{1}{c}{TEL} & \multicolumn{1}{c}{TUR}	& \multicolumn{1}{c}{\bf P (\%)} & \multicolumn{1}{c}{\bf R (\%)}  \\			
      \cline{2-14} %\hline
ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0  \\
CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0  \\
\cline{2-14}
FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0  \\
GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0  \\
\cline{2-14}
HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0  \\
ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0   \\
\cline{2-14}
JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 \\
KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0  \\
\cline{2-14}
SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0  \\
TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0   \\
%\hline
TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0   \\
			\cline{2-14}%\hline
\end{tabular}
\end{center}
\begin{center}
Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%.\\
\end{center}

@@

\begin{center}\small
\begin{tabular}{|l|r|c|}
      %\hline
 \multicolumn{1}{p{9em}}{Main features} &  \multicolumn{1}{c}{\# Params}	&  \multicolumn{1}{c}{Accuracy (\%)}	\\				
       \hline %\hline
\feat{POS} & 540,947 & 55.18 \\
+ \feat{FreqChar} & 1,036,871 & 79.55 \\ 
\quad + \feat{CharPrompt} & 2,111,175 & 79.82 \\ 
\qquad + \feat{Brown} & 5,664,461 & 81.09 \\
			\hline%\hline
\end{tabular}
\end{center}

\begin{center}\small
\begin{tabular}{|l|c|c|}
      %\hline
 \multicolumn{1}{p{9em}}{Additional features} & \multicolumn{1}{c}{\# Params} & \multicolumn{1}{c}{Accuracy (\%)}	\\				
       \hline %\hline
\textsc{main} & 5,664,461 & 81.09 \\
%\textsc{main} + \feat{Position} & 6,153,015 & 81.00 \\
\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 \\
\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09  \\
%\textsc{main} + \feat{Pron} & 5,664,736 & 81.09  \\
\textsc{main} + \feat{Punct} & 5,664,604 & 81.09  \\
\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27  \\
\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
\textsc{full model} & - & {\bf 84.55} \\

>>>>

\begin{description}
\item [Part-of-speech (POS) $n$-grams] Counts of every POS 1-, 2-, and 3-gram in each document. %53.92\% 
\item [FreqChar] Counts of character 1--4-grams that are observed more than 5 times in the training corpus.
\item [CharPrompt] Conjunction of the FreqChar features with the prompt ID %65.09
\item [Brown clusters] We clustered 8~billion words of English into 600~clusters and used 1--4-grams.
\item[PsvRatio] The proportion of passive verbs out of all verbs.
\item[DocLen] Document length in tokens.
\item[Punct] Counts of each punctuation mark. 
\item[Misspell] Spelling correction edits. Features included substitutions, deletions, insertions and joinings.% as well as the word position where the error occurred.
\item[Restore] Substitutions, deletions and
  insertions of common words that were restored with an $n$-gram LM.
\item[CxtFxn] Contextual function words. Counts of $n$-grams consisting of one or two function words and the POS tag of the adjacent words: {\tt CHI:<some JJ>}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Results%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Results}{name=results,column=1.15,span=1.85,below=example}{
\begin{center}
\small
\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r||c|c|}
      %\hline
 \multicolumn{1}{c}{\emph{true}$\downarrow$} & \multicolumn{1}{c}{ARA} & \multicolumn{1}{c}{CHI} & \multicolumn{1}{c}{FRE} & \multicolumn{1}{c}{GER} 
 & \multicolumn{1}{c}{HIN} & \multicolumn{1}{c}{ITA} & \multicolumn{1}{c}{JPN} &  \multicolumn{1}{c}{KOR} & \multicolumn{1}{c}{SPA} 
 &  \multicolumn{1}{c}{TEL} & \multicolumn{1}{c}{TUR}	& \multicolumn{1}{c}{\bf P (\%)} & \multicolumn{1}{c}{\bf R (\%)}  \\			
      \cline{2-14} %\hline
 ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0  \\
CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0  \\
\cline{2-14}
FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0  \\
GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0  \\
\cline{2-14}
HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0  \\
ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0   \\
\cline{2-14}
JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 \\
KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0  \\
\cline{2-14}
SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0  \\
TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0   \\
%\hline
TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0   \\
			\cline{2-14}%\hline
\end{tabular}
\end{center}
\begin{center}
Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%.\\
\end{center}

@@

\begin{center}\small
\begin{tabular}{|l|r|c|}
      %\hline
 \multicolumn{1}{p{9em}}{Main features} &  \multicolumn{1}{c}{\# Params}	&  \multicolumn{1}{c}{Accuracy (\%)}	\\				
       \hline %\hline
\feat{POS only} & 540,947 & 55.18 \\
+ \feat{FreqChar} & 1,036,871 & 79.55 \\ 
\quad + \feat{CharPrompt} & 2,111,175 & 79.82 \\ 
\qquad + \feat{Brown} & 5,664,461 & 81.09 \\
\feat{Brown only} & 1,240,420 & 72.26 \\
			\hline%\hline
\end{tabular}
\end{center}

\begin{center}\small
\begin{tabular}{|l|c|c|}
      %\hline
 \multicolumn{1}{p{9em}}{Additional features} & \multicolumn{1}{c}{\# Params} & \multicolumn{1}{c}{Accuracy (\%)}	\\				
       \hline %\hline
\textsc{main} & 5,664,461 & 81.09 \\
%\textsc{main} + \feat{Position} & 6,153,015 & 81.00 \\
\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 \\
\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09  \\
%\textsc{main} + \feat{Pron} & 5,664,736 & 81.09  \\
\textsc{main} + \feat{Punct} & 5,664,604 & 81.09  \\
\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27  \\
\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
\textsc{full model} & 8,312,205 & {\bf 84.55} \\
